\huge \systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-22 misc2.tex
Improvements

\begin{alertblock}{Wake/Sleep DSL Induction}
  \flushleft
  \textbf{Domain Specific Language (DSL):}
  A finely-tuned program representation, specialized to a domain of programming tasks.
  Prior work in program learning  largely uses hand-engineered DSLs.

@@

  \textbf{Program representation:}
  $\approx $Lisp; conditionals, variables, $\lambda$~abstraction

@@

\begin{tikzpicture}[scale=4,line width=1.5mm]

  \node[latent,scale=3] at (3.5,3) (dx){$\mathcal{D}$};
  \node[latent,scale=3] at ([xshift=2cm]dx) (zp){$p_n$};
  \node[obs,scale=3] at ([xshift=2cm]zp) (xp) {$x_n$};
  \plate {}{(zp)(xp)}{};
%  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.east) {(b) \\recognition model};
  \draw [->,red] (xp.south) to[out = -90,in = -90] node(nn){} (zp.south);
%  \draw [->,red] (tx.west) -- (zp.east);
  \draw [->] (dx.east) -- (zp.west);
  \draw [->] (zp.east) -- (xp.west);

  \node at (nn) {
    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.5,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}
  };
  \node[shift={+(0,-1.7)}] at (nn) { $Q$  };

  \end{tikzpicture}

@@

  \textbf{Likelihood model} $\probability[x_n|p_n]$
  scores program $p_n$ on task $x_n$

@@

  \begin{itemize}
  \item \textbf{Samples (``Dreams'') from DSL}: Unlimited data, but only high-quality if generative model $\mathcal{D}$ is good. Like Helmholtz Machine's recognition model training. Loss:
    \begin{equation*}
\expect_{(p,x)\sim\mathcal{D} }\left[\log Q(p|x)\right]
      \end{equation*}
  \item \textbf{Self-Supervised}: $(x_n,p_n)$ pairs discovered during waking. Loss:
    \begin{equation*}
 %\sum_{n = 1}^N\left[\sum_{(x_n,p_n)}
  \frac{\probability\left[x_n,p_n|\mathcal{D}\right]}{\sum_{(x_n,p_n')}\probability\left[x_n,p_n|\mathcal{D} \right]}\log Q(p_n|x_n)%\right]
      \end{equation*}
  \end{itemize}

@@

@@

\begin{block}{Generative models of images: Turtle/LOGO Graphics}

  \newcommand{\dreamSize}{5.5cm}
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{12 (of 136) Tasks}}\\\hline
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_3_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow1_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow2_random_1.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/hexa_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_5_h.png}\\
        \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/star_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/spiral6_h.png}&
        \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_7_h.png}\\

%    \includegraphics[width = \dreamSize]{turtleTasks/circle/trimmed/train_circle_10_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/smooth_spiral4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/los/trimmed/train_los_3_1_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/iter2_h.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
  \end{tabular}\hspace{4cm}%
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{9 samples from learned DSL}}\\\hline
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/4361002260.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5809723215.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5818934795_norm.png}\\
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6027771181.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1950268419.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6770710484.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7045328293.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7623700519.png}&
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/8879622788.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9150025422.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9666602433.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
  \end{tabular}

  \vspace{2cm} \textbf{Left:}  Agent controls a `pen' -- tasked with drawing pictures. \textbf{Right:} During Sleep-R,
   `dream' by sampling programs from learned DSL and rendering them.

>>>>

\begin{alertblock}{Wake/Sleep DSL Induction}
  \flushleft
  \textbf{DSL:}
  Domain Specific Language, a finely-tuned program representation, specialized to a domain of programming tasks.
  Prior work in program learning  largely uses hand-engineered DSLs.

@@

  \textbf{Program representation:}
  $\approx $~Lisp; conditionals, variables, $\lambda$~abstraction

@@

  \includegraphics{figures/animation/DC.eps}

@@

  \textbf{Likelihood model} $\probability[x_n|p_n]$
  scores program $p_n$ on task $x_n.

@@

  \begin{itemize}
  \item \textbf{``Dreams'' from DSL}: Can sample unlimited data, quality
    positively correlates with fitness of generative model $\mathcal{D}$. Like Helmholtz Machine's recognition model training. Loss:
    \begin{equation*}
\expect_{(p,x)\sim\mathcal{D} }\left[\log Q(p|x)\right]
      \end{equation*}
  \item \textbf{Self-Supervised}: $(x_n,p_n)$ pairs discovered during waking. Loss:
    \begin{equation*}
 %\sum_{n = 1}^N\left[\sum_{(x_n,p_n)}
  \frac{\probability\left[x_n,p_n|\mathcal{D}\right]}{\sum_{(x_n,p_n')}\probability\left[x_n,p_n|\mathcal{D} \right]}\log Q(p_n|x_n)%\right]
      \end{equation*}
  \end{itemize}

@@

\begin{column}{\twocolwid} % The first column within column 2 (column 2.1)

@@

\end{column}
\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)

\begin{block}{Bootstrapping}

\begin{figure}
\hspace*{-1.5cm}  \begin{tikzpicture}[scale=3,line width=1.5mm]
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs: $p$};
    \node[align = center](DSL) at (3,1) {DSL: $\mathcal{D}$};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model: $Q$};

    \draw [->] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-G)}} (DSL.30);
    \draw [->] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.150);
    \draw [->] (DSL.east) to[out = -30,in = 210] node[above, align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.west);

    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
 % \caption{\system solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
\end{figure}
%% \begin{itemize}
%% \item Search finds new programs$\implies$ DSL+recognition model get more data
%% \item DSL improves$\implies$easier search, recognition model gets better data
%%   \item Recognition model improves$\implies$ easier search
%%   \end{itemize}

\end{column}
\end{columns}

\begin{block}{Generative models of images: \texttt{Turtle}s all the way down}

Agent controls a `pen' tasked with drawing pictures.

  \includegraphics[width=20cm]{figures/poster2/sampleTasks.png}
